Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
Hurricane History Done

\section{Executive Summary}
\label{sec:summary}
\\
Governor Bryant,\\

@@

\section{Historical Hurricane Trends}
\label{sec:hurricanes}
  \par
    Northwest

@@

@@

  \begin{thebibliography}{9}
    \bibitem{county_map}
      \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}
    \bibitem{ms_highways}
      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
    \bibitem{pmc}
      \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
    \bibitem{5news}
      \url{http://5newsonline.com/2012/08/27/garretts-blog-hurricanes-in-arkansas/}
    \bibitem{famsize}
      \url{http://www.statista.com/statistics/183657/average-size-of-a-family-in-the-us/}
    \bibitem{graphtool}
      \url{http://graph-tool.skewed.de/}
    \bibitem{census}
      \url{http://census.ire.org/data/bulkdata.html}
  \end{thebibliography}

>>>>

\section{Executive Summary}
\label{sec:summary}
\vspace{1cm}
Governor Bryant,\\

@@

\section{Historical Hurricane Trends}
\label{sec:hurricanes}
  Before designing potential evacuation strategies, we first sought to understand the expected speed, size, and landfall of a hurricane impacting Mississippi. Discovering patterns in these storms proved very difficult, because the Earth's atmosphere is a chaotic system. Other than the general pattern that hurricanes in the Gulf of Mexico tend to curl back toward the north-east, there is very little we can predict about a hurricane's trajectory:
   \begin{figure}[H]
    \centering
      \includegraphics[width=.5\textwidth]{figures/chaos.jpg}
      \caption{Map of Atlantic Hurricane Trajectories \cite{chaos}}
    \end{figure}
  As a result of this, we decided to test our evacuation plans against hurricanes that actually occurred in the past. This ensures that our model parameters governing the hurricane are as accurate as possible. In order to do this, we parsed a NOAA dataset containing every cyclone (tropical storm, hurricane, etc.) occurring from 1851 to 2014. For each hurricane in this dataset, we found the first latitude and longitude datapoint over Mississippi and recorded that as a landfall position (throwing out hurricanes that never passed over Mississippi). You can see these points in the figures below, where the left is a web-app display of hurricane trajectories over Mississippi, while the right is the 15 discovered landfalls we pulled from the NOAA dataset:
    \begin{figure}[H]
      \center
      \begin{subfigure}[b]{0.5\textwidth}
        \center
        \includegraphics[width=\linewidth]{figures/smaller_chaos.png}
        \caption*{Map of Mississippi Hurricane Trajectories \cite{smaller_chaos}}
      \end{subfigure}~
      \begin{subfigure}[b]{0.5\textwidth}
        \center
        \includegraphics[width=\linewidth]{figures/parsed_chaos.png}
        \caption*{Landfall Locations Parsed From Hurricane Dataset \cite{fifteen}}
      \end{subfigure}
    \end{figure}
    \newpage
  Each point in this dataset had an associated wind speed that we used to classify it's category \cite{categories}:
  \begin{itemize}
    \item[]
      \textbf{Category 1:} 74-95 mph
    \item[]
      \textbf{Category 2:} 96-110 mph
    \item[]
      \textbf{Category 3:} 111-129 mph
    \item[]
      \textbf{Category 4:} 130-156 mph
    \item[]
      \textbf{Category 5:} 157 mph or higher
  \end{itemize}
  The last piece of data we needed for these hurricanes were their radii. Since hurricane radii records don't exist for years earlier than 2004, we used a least squares linear fit to interpolate the radius for a given hurricane wind speed:
  \begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{figures/least_fit.png}
    \caption{Hurricane Radius (nmi) vs Wind Speed (kt)}
    \label{fig:highway_map}
  \end{figure}

@@

    \begin{figure}[H]

@@

  \begin{thebibliography}{9}
    \bibitem{county_map}
      \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}
    \bibitem{ms_highways}
      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
    \bibitem{chaos}
      \url{http://www.mapcruzin.com/images/hurricane-shapefile-400x255.png}
    \bibitem{smaller_chaos}
      \url{https://coast.noaa.gov/hurricanes/}
    \bibitem{fifteen}
      \url{http://www.aoml.noaa.gov/hrd/hurdat/Data_Storm.html}
    \bibitem{categories}
      \url{http://www.nhc.noaa.gov/aboutsshws.php}

    \bibitem{pmc}
      \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
    \bibitem{5news}
      \url{http://5newsonline.com/2012/08/27/garretts-blog-hurricanes-in-arkansas/}
    \bibitem{famsize}
      \url{http://www.statista.com/statistics/183657/average-size-of-a-family-in-the-us/}
    \bibitem{graphtool}
      \url{http://graph-tool.skewed.de/}
    \bibitem{census}
      \url{http://census.ire.org/data/bulkdata.html}
  \end{thebibliography}
